On the probability of finding nonphysical solutions through shadowing\tnoteref{1}

### 2020-12-12 main_els.tex
First para of intro complete.

\section{Introduction}
In this paper, we show that a large mismatch is possible in the ensemble averages of two slightly different chaotic systems. We illustrate this feature of chaotic dynamics by studying the long-time behavior of {\em shadowing} solutions in analytically or numerically constructed examples.{\em Shadowing} solutions are true orbits that closely follow a slightly perturbed solution, say due to a small parameter perturbation in the original governing equation, for a long, and sometimes infinitely long, time. In this paper, we show through rigorous analytical and numerical examples that these shadowing orbits can be statistically mismatched. In other words, the probability distribution of shadowing orbits is different, often drastically so, from that of almost every solution.

>>>>

\section{Introduction}
In this paper, we show that a large mismatch is possible in the long-time or statistical behavior of two slightly different chaotic systems. We illustrate this feature of chaotic dynamics by studying long-time averages along {\em shadowing} solutions in analytically or numerically constructed 
examples. Shadowing solutions are true orbits of a dynamical system that closely follow slightly perturbed orbits, or {\em pseudo-orbits},  for a long, and sometimes infinitely long, time. In this paper, we show through rigorous analytical and numerical examples that shadowing orbits may not represent the long-time behavior of almost every orbit. In other words, the probability distribution of shadowing orbits is different, often drastically so, from that of almost every solution of the unperturbed system. The pseudo-orbits we study are solutions to slightly different governing equations that are generated by small parameter perturbations of the original system. Because we show that shadowing solutions following these pseudo-orbits almost surely have different statistics when compared to an ensemble of unperturbed orbits, we prove that small parameter perturbations can produce a large statistical mismatch between the perturbed and unperturbed systems.
